Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2018-04-02 removals/Manuscript/appendix.tex
Added better than Jensen section

>>>>

\subsection{Correcting for Jensen's inequality in one-step-ahead projections}

We used an individual-based model, based on the vital rate regressions, to project total cover one-year ahead in each quadrat. We modeled expected growth and variance in growth on the log scale, meaning that when we exponentiate to transform cover into arithmetic space the expected variance in cover is not normally distributed, and Jensen's inequality creates a downward bias in predicted cover. Therefore, we developed a correction that takes into account the relationship between plant size and expected variance in growth.

 After the growth model is fitted,

 \begin{enumerate}
 \item  Extract for each plant in the data set (indexed by $k$) 
 its \texttt{logarea.t0} $z_{0,k}$, the growth residual $z_{1,k} - \hat{z}_{1,k}$ (here $z_1$ is
 the plant's \texttt{logarea.t1} and $\hat{z}_1$ is the predicted logarea), and the predicted variance
 in growth $V_k$.

 \item Compute the set of scaled residuals $r_k = (z_{1,k} - \hat{z}_{1,k})/\sqrt{V_k}$ and store them
 in a vector \texttt{scaledResiduals}.

 \end{enumerate}

 Then in computing the one-step-ahead predictions, for each growth model the line 
 \begin{verbatim}
 plants$area.pred <- plants$surv.prob*exp(plants$logarea.pred + V.pred/2)
 \end{verbatim} 
 is replaced by the following 
 \begin{verbatim}
 resid.Pred <- sqrt(V.pred)*scaledResiduals
 newJensen <- mean(exp(resid.Pred))
 plants$area.pred <- plants$surv.prob*exp(plants$logarea.pred)*newJensen
 \end{verbatim}
